PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2022-09-07 main.tex
Fix up figure 8

In figure \ref{fig: surfden_b}, we plot the masses of the resulting protoplanets and planetesimals in all four simulations in units of $\tilde{b}$ (see equation \ref{eq:iso}). Here, we assume that each embryo has reached its isolation mass, and that differences in mass are driven by differences in the initial surface density at the embryo's current location, along with the size of its feeding zone, which is set by the dynamics relevant at that location in the disk. By plotting the derived value of $\tilde{b}$ as a function of orbital period, differences in the dynamical interactions at different locations of the disk are made more clearly visible. As mentioned previously, $\tilde{b} = 2 \sqrt{3}$ (indicated by the horizontal dashed line) carries a special significance, being the minimum feeding zone width that a body can have. In all four simulations, the feeding zone width exceeds the minimum value in the inner disk and approaches $2 \sqrt{3}$ beyond $\sim$ 60 days. The orbital periods at which this transition occurs are remarkably similar, despite the vastly different solid surface density profiles used. This similarity indicates that the boundary between accretion modes is not dependent upon the surface density profile chosen, and also supports our conclusion that planetesimal accretion is largely complete everywhere in the disk.

>>>>

In figure \ref{fig:surfden_b}, we plot the masses of the resulting protoplanets and planetesimals in all four simulations in units of $\tilde{b}$ (see equation \ref{eq:iso}). Here, we assume that each embryo has reached its isolation mass, and that differences in mass are driven by differences in the initial surface density at the embryo's current location, along with the size of its feeding zone, which is set by the dynamics relevant at that location in the disk. By plotting the derived value of $\tilde{b}$ as a function of orbital period, differences in the dynamical interactions at different locations of the disk are made more clearly visible. As mentioned previously, $\tilde{b} = 2 \sqrt{3}$ (indicated by the horizontal dashed line) carries a special significance, being the minimum feeding zone width that a body can have. In all four simulations, the feeding zone width exceeds the minimum value in the inner disk and approaches $2 \sqrt{3}$ beyond $\sim$ 60 days. The orbital periods at which this transition occurs are remarkably similar, despite the vastly different solid surface density profiles used. This similarity indicates that the boundary between accretion modes is not dependent upon the surface density profile chosen, and also supports our conclusion that planetesimal accretion is largely complete everywhere in the disk.
